---
title: "HTML_Tutorial"
author: "Kunyelewosi Alexander"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

This is a tutorial on how to use rmarkdown for reproducible research

Here we an type long passages or descriptions for our data without the need of "hashing" out our comments with the # symbol. In our first example, we will be using the ToothGrowth dataset. In this experiment, Guinea Pigs (literal) were given different amounts of Vitamin C to see the effect on the growth rate of the animal's teeth.

To run R code in a markdown file, we need to denogte the section that is considered R code. We call these "code chunks"

Below is a code chunk

```{r}
ToothData <- ToothGrowth
head(ToothData)
```

As you can see, from the running the "play" button of the code chunk, the the results are printed inline of the r markdown

```{r}
fit <- lm(len ~ dose, data=ToothData)

b <- fit$coefficients
 
plot(len ~ dose, data = ToothData)

abline(lm(len ~ dose, data = ToothData))
```

The slope of our regression line is `r b[2]`.