---
title: "HTML_Tutorial"
author: "Kunyelewosi Alexander"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

This is a tutorial on how to use rmarkdown for reproducible research

Here we an type long passages or descriptions for our data without the need of "hashing" out our comments with the # symbol. In our first example, we will be using the ToothGrowth dataset. In this experiment, Guinea Pigs (literal) were given different amounts of Vitamin C to see the effect on the growth rate of the animal's teeth.

To run R code in a markdown file, we need to denogte the section that is considered R code. We call these "code chunks"

Below is a code chunk

```{r}
ToothData <- ToothGrowth
head(ToothData)
```

As you can see, from the running the "play" button of the code chunk, the the results are printed inline of the r markdown

```{r}
fit <- lm(len ~ dose, data=ToothData)

b <- fit$coefficients
 
plot(len ~ dose, data = ToothData)

abline(lm(len ~ dose, data = ToothData))
```

The slope of our regression line is `r b[2]`.

# Setion Headers

We can also put sections and subsections in our r markdown file, similar to numbers or bullet points in a word document. This is done with the "#" that we previously used to denote ext in R script

# First level header
## Second level header
### Third level header

Make sure that you put space after the "#", otherwise, it will not work

We can also add bullet point-type marks in our r markdown file

- one item
- one item
- one item
  - one more item
  - one more item
  - one more item
    - one last

It's important to note here that in R Markdown, indentation matters!

1. First Item
2. Second Item
3. Third Item
  a. Sub Item 1
  b. Sub Item 2
  c. Sub Item 3

## Block Quotes

We can really put nice quotes into the markdown document. We do this using the ">" symbol.

> "Genes are like the story, and DNA is the language that the story is written in."
>
> ---Sam Kean
 
## Hyperlinks

Hyperlinks can also be incorporated into these files. This is especially useful in HTML files, since they are in a web browser and will direct the reader to the material that you are interested in showing them. Here, we will used the link to R Markdown's homepage for this example

[RMarkdown](http://rmarkdown.rstudio.com/)

## Formulas

We can also put nice formatted formulas into r markdown using two dollar signs

$$p^2 + 2pq + q^2 = 1$$

And you can get really complex as well

$$\Theta = \begin{pmatrix}\alpha and \beta\\
\gamma & \delta
\end{pmatrix}$$